### 2021-04-21 README.Rmd
sfss

`{steveproj}` is an R package to help you start and manage R projects with an eye toward producing an academic project (to culminate in an academic paper). The package is in development and will incorporate other packages in my eponymous R ecosystem, prominently [`{stevetemplates}`](https://github.com/svmiller/stevetemplates). The package itself leans primarily on Rstudio and how it creates/manages projects. The creation a project in Rstudio, through `{steveproj}`, will result in a new directory containing subdirectories for rendering documents (`src`), R scripts for analysis (`R`), finished data objects (`data`), and finished reports (`doc`). An accompanying `Makefile` and R Markdown file will assist in the management and production of the project.

@@

### A Comment on Make and Rstudio

The functions in this package work as intended in an R console, but this package realizes its full potential and its core functions are fully augmented through two additional pieces of software the user should already have installed. The first is [Rstudio](https://www.rstudio.com). Most dedicated R users are likely fully aware of Rstudio as an integrated desktop environment (IDE) and already have it installed and pre-configured to what they think is ideal for their workflow. I will only add that I think it advantageous for the sake of this package to adjust the pane layout such that the "source" pane is top left, the "console" pane is top right, the "environment" pane is bottom left, and the "files" pane is bottom right.

The second piece of software the user should install is [Make](https://en.wikipedia.org/wiki/Make_(software)). Make is a build automation tool built around a "Makefile", which contains a set of recipes that have various targets and dependencies. For each target, if the specified dependency is "newer" than the target (or if the target does not yet exist), the Makefile executes a command. Users will get a reproducible example of how this works, and they can learn by example from it, but it assumes the user already has it installed.

@@

Windows users will invariably have to install it since it will not come by default. [*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) has a guide and installer to do this. Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users. Afterward, a simple `choco install make` command should work just fine. The increased integration of Linux into Windows, prominently [Windows Subsystem for Linux](https://docs.microsoft.com/en-us/windows/wsl/install-win10), offers more avenues for Windows users to install Make on their operating system.

>>>>

`{steveproj}` is an R package to help you start and manage R projects with an eye toward producing an academic project (to culminate in an academic paper). The package is in development and will incorporate other packages in my eponymous R ecosystem, prominently [`{stevetemplates}`](https://github.com/svmiller/stevetemplates). The package itself leans primarily on Rstudio and how it creates/manages projects. The creation a project in Rstudio, through `{steveproj}`, will result in a new directory containing subdirectories for rendering documents (`src/`), R scripts for analysis (`R/`), finished data objects (`data/`), and finished reports (`doc/`). An accompanying `Makefile` and R Markdown file will assist in the management and production of the project.

@@

### A Comment on LaTeX, Make, and Rstudio

The functions in this package work as intended in an R console, but this package realizes its full potential and its core functions are fully augmented through three additional pieces of software the user should already have installed. The first is [Rstudio](https://www.rstudio.com). Most dedicated R users are likely fully aware of Rstudio as an integrated desktop environment (IDE) and already have it installed and pre-configured to what they think is ideal for their workflow. I will only add that I think it advantageous for the sake of this package to adjust the pane layout such that the "source" pane is top left, the "console" pane is top right, the "environment" pane is bottom left, and the "files" pane is bottom right.

The second piece of software is [LaTeX](https://www.latex-project.org). LaTeX is a prominent document preparation system in academia and preferred by publishers especially for its contrast to "What You See Is What You Get" word processors like Microsoft Word. `{steveproj}` ultimately places R Markdown and Pandoc---which are necessary for this package---before LaTeX in terms of document preparation. No matter, `{steveproj}` necessarily elevates LaTeX PDF documents above other output types. Interested users with no awareness of LaTeX should know `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`. This would install and maintain a version of LaTeX to compile these documents. However, the particular flavor of LaTeX template (from `{stevetemplates}`) requires one additional LaTeX dependency that `{tinytex}` does not install by default. You may encounter a vague error in rendering to PDF that reads something like this.

> ! Undefined control sequence.
l.40 \urlstyle
{same} % disable monospaced font for URLs

If you encounter this error, run the following command in your R console.

```r
tinytex::tlmgr_install("xurl")
```

[This should fix it](https://github.com/svmiller/stevetemplates/issues/1). I thank Ian Adams for bringing this to my attention (and Cornelius Hennch for proposing a solution).

The third piece of software the user should install is [Make](https://en.wikipedia.org/wiki/Make_(software)). Make is a build automation tool built around a "Makefile", which contains a set of recipes that have various targets and dependencies. For each target, if the specified dependency is "newer" than the target (or if the target does not yet exist), the Makefile executes a command. Users will get a reproducible example of how this works, and they can learn by example from it, but it assumes the user already has it installed.

@@

Windows users will invariably have to install it since it will not come by default. [*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) and installer to do this. Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users. Afterward, a simple `choco install make` command should work just fine. The increased integration of Linux into Windows, prominently [Windows Subsystem for Linux](https://docs.microsoft.com/en-us/windows/wsl/install-win10), offers more avenues for Windows users to install Make on their operating system.
